Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2021-05-11 2021/emnlp/auto_cl_mdmt.tex
reviewed till section 5

\subsection{Experimental tasks}
We evaluate the efficacy of our methods compared to several aforementioned baselines via 5 tasks including domain adaptation; multi-domain adaptation, bi-domain adaptation, unseen domain adaptation, and unsupervised domain adaptation.

In the domain adaptation task, given the data of 6 domains including \domain{med}, \domain{bank}, \domain{law}, \domain{it}, \domain{talk}, \domain{rel}, we aim to build expert NMT models for each domain respectively.

In the multi-domain adaptation task, given the data of 6 domains, we aim to build an NMT model which gives the best performance regarding a predefined test set containing equivalently 6 domains.

In the bi-domain adaptation task, given the data of 6 domains, we only focus on 2 domains of them.

In the fourth experiment, given the data of 6 domains and a small dev set of an unseen domain, which is News, in this case, we aim to build an NMT model which is robust to the unseen domain.

In the unsupervised domain adaptation task, we cluster the training data of 6 domains into 30 clusters using the KNN algorithm in the same way as in the work of \citet{Tars18multidomain}, then adapt these clusters to one of 6 domains given the corresponding in-domain dev set. We compare MDAC to DDS over 6 domains.

>>>>

\subsection{Experimental tasks}
We evaluate and compare our method with multiple baselines in 5~tasks including: domain adaptation; multi-domain adaptation, bi-domain adaptation, unseen domain adaptation, and unsupervised domain adaptation.

In the domain adaptation task, given the data from 6 domains (\domain{med}, \domain{bank}, \domain{law}, \domain{it}, \domain{talk}, \domain{rel}), we aim to build distinct expert NMT models for each domain.

In the multi-domain adaptation task, given the same 6 domains, we aim to build one single NMT model that would perform optimally assuming a uniform distribution of domains during the test.

In the bi-domain adaptation task, given again same 6 domains, we only focus on adapating only to 2 domains.

In the fourth experiment, given training data in 6 domains and a small development set of an new domain, (\domain{News} in our case) we aim to build an NMT model which will perform well on test data from the unseen domain.

Finally, in the unsupervised domain adaptation task, we cluster all available training data into 30 clusters using the KNN algorithm in the same way as in the work of \citet{Tars18multidomain}, then adapt these clusters to one of 6 domains given the corresponding in-domain dev set. We compare MDAC to DDS over 6 domains.
